Classical Planning with Simulations: \\ Results on the Atari Video Games

### 2015-02-05 ijcai15-paper/paper.tex
Typo fixed in Table caption
Tweaks to comments about width-based vs. RL

 \caption{\small Performance that results form various  lookahead algorithms in \numgames\  Atari games. The algorithms, \BRFS, $\IW(1)$, \BFS, and \UCT, are evaluated
 over $10$ runs (episodes) for each game. 
The maximum episode duration is  $18,000$  frames and every algorithm is limited to a lookahead budget of 150,000 simulated frames.
Figures for \BRFS\ and \UCT\ taken from Bellemare et al. Average  CPU times per action in seconds, rounded to nearest integer, shown for  $\IW(1)$ and \BFS. 
Numbers  in bold show best performer in terms of average score, while numbers shaded in light grey show scores  that are better than \UCT's. 
Bottom part of the table shows pairwise comparisons among the algorithms.}
\label{performance}
\end{table*}

@@

$\IW(1)$ also outperforms the best learning algorithm in
\cite{deep-mind-atari} in the $7$ games considered there, and
\BFS\ does so in $6$ of the $7$ games. Comparing with the scores reported for the reinforcement learning algorithms by BNVB,
we note that both $\IW(1)$ and \BFS\ do much better than the best learning algorithm in
those games where the learning algorithms outperform \UCT\ like \Montezuma, \Venture\
and \Bowling.  In \Montezuma\ rewards are very
sparse, deep, and most of the actions lead to losing a life with
no immediate penalty or consequence.  All algorithms achieve $0$ score, 
except for \BFS\ that achieves an average score of $540$, and a score
of $2500$ in one of the runs. This means however that even \BFS\  is not able to 
consistently find rewards in this game. This game and several others
like \Breakout\ and \SpaceInvaders\ could be much simpler by adding
negative rewards for losing a life. We have indeed observed that
our planning algorithms do not care much about losing lives
until there is just one life left, when their play noticeably improves.
This can be seen in the videos mentioned above, and suggest a simple form of learning that would be useful to both planners
and reinforcement learning algorithms.

>>>>

 \caption{\small Performance that results from various  lookahead algorithms in \numgames\  Atari games. The algorithms, \BRFS, $\IW(1)$, \BFS, and \UCT, are evaluated
 over $10$ runs (episodes) for each game. 
The maximum episode duration is  $18,000$  frames and every algorithm is limited to a lookahead budget of 150,000 simulated frames.
Figures for \BRFS\ and \UCT\ taken from Bellemare et al. Average  CPU times per action in seconds, rounded to nearest integer, shown for  $\IW(1)$ and \BFS. 
Numbers  in bold show best performer in terms of average score, while numbers shaded in light grey show scores  that are better than \UCT's. 
Bottom part of the table shows pairwise comparisons among the algorithms.}
\label{performance}
\end{table*}

@@

$\IW(1)$ obtains better scores than the best learning algorithm in
\cite{deep-mind-atari} in the $7$ games considered there, and
\BFS\ does so in $6$ of the $7$ games. Comparing with the scores reported for the reinforcement learning algorithms in BNVB,
we note that both $\IW(1)$ and \BFS\ do much better than the best learning algorithm in
those games where the learning algorithms outperform \UCT\, namely, \Montezuma, \Venture\
and \Bowling. We take this as evidence that $\IW(1)$ and \BFS\ are as at least as good as learning
algorithms at finding rewards in games where \UCT\ is not very effective.

For instance, in \Montezuma\ rewards are very sparse, deep, and most of the actions lead to losing a life with
no immediate penalty or consequence.  In our experiments, all algorithms achieve $0$ score, 
except for \BFS\ that achieves an average score of $540$, and a score
of $2,500$ in one of the runs. This means however that even \BFS\  is not able to 
consistently find rewards in this game. This game and several others
like \Breakout\ and \SpaceInvaders\ could be much simpler by adding
negative rewards for losing a life. We have indeed observed that
our planning algorithms do not care much about losing lives
until there is just one life left, when their play noticeably improves.
This can be seen in the videos mentioned above, and suggest a simple form of learning that would be useful to both planners
and reinforcement learning algorithms.
